Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-17 1-Main.tex
format and cleaning
Updates from Overleaf
OpenFlexo -> Openflexo

\begin{document}
\begin{article}{
%\title{\mpc: the FML solution}
\title{Multi-level modelling with Openflexo/FML - A contribution to the \mpc}

%% Group authors per affiliation:
%\author{Sylvain Guérin, Joel Champeau}
%\address{ENSTA Bretagne}

%\author{Jean-Christophe Bach, Salvador Martinez, Antoine Beugnard, Fabien Dagnat}
%\address{IMT Atlantique}

%% or include affiliations in footnotes:
\author*{Sylvain Guérin}{firstname.lastname@ensta-bretagne.fr}
\address{ENSTA Bretagne, Lab-STICC, UMR 6285, Brest, France}
%\ead{firstname.lastname@ensta-bretagne.fr}

@@

\author{Jean-Christophe Bach}
\address{IMT Atlantique, Lab-STICC, UMR 6285, F-29238 Brest, France}
%\ead{firstname.lastname@imt-atlantique.fr}

@@

\abstract{\input{2-Abstract}}
\keywords{Multilevel Modeling Challenge, Federation Modeling Language, OpenFlexo}
\bibliography{biblio.bib}

}
%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.

@@

\end{article}
\end{document}
%%

>>>>

\DeclareTextFontCommand{\mytexttt}{\ttfamily\hyphenchar\font=45\relax}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\begin{document}
\begin{article}{
    % \title{\mpc: the FML solution}
    \title{Multi-level modelling with Openflexo/FML - A contribution to the \mpc}

    %% or include affiliations in footnotes:
    \author*{Sylvain Guérin}{firstname.lastname@ensta-bretagne.fr}
    \address{ENSTA Bretagne, Lab-STICC, UMR 6285, Brest, France}
    % \ead{firstname.lastname@ensta-bretagne.fr}

@@

    \author{Jean-Christophe Bach}
    \address{IMT Atlantique, Lab-STICC, UMR 6285, F-29238 Brest, France}
    % \ead{firstname.lastname@imt-atlantique.fr}

@@

    \abstract{\input{2-Abstract}}
    \keywords{Multilevel Modeling Challenge, Federation Modeling Language, OpenFlexo}
    \bibliography{biblio.bib}
}

@@

\end{article}

\end{document}
%%
